# Data structure {}

Here, all data files used for the analyses are described. The tables are available under `https://github.com/buerap/master_thesis`.

## Observational units {}
### Characteristics {}
The described columns are available in the raw data file `raw_pos_characteristics.csv`, which contains information on the observational units.
```{r tidy = FALSE, echo = FALSE}
knitr::kable(
  raw_pos_char,
  booktabs = TRUE
)
```

### Soil temperatures and snowmelt patterns {}
The described columns are available in the data file `R_pos_temperature.csv`, which contains thermal properties as well as information on snowmelt patterns at the observational units.
```{r tidy = FALSE, echo = FALSE}
knitr::kable(
  R_pos_temp,
  booktabs = TRUE
)
```

### Soil moisture {}
The described columns are available in the data file `raw_moistmeasure_moisture.csv`, which contains soil moisture measurements at the observational units.
```{r tidy = FALSE, echo = FALSE}
knitr::kable(
  raw_moist,
  booktabs = TRUE
)
```

### Soil properties {}
The described columns are available in the data file `raw_pos_soil.csv`, which contains information on soil analyses from each observational unit.
```{r tidy = FALSE, echo = FALSE}
knitr::kable(
  raw_soil,
  booktabs = TRUE
)
```

### Vegetation {}
The described columns are available in the data file `raw_pos_vegetation.csv`, which contains data from vegetation surveys at the observational units.
```{r tidy = FALSE, echo = FALSE}
knitr::kable(
  raw_pos_veg,
  booktabs = TRUE
)
```

Vegetation survey data can be joined with species information data. The described columns are available in the data file `raw_species_information.csv`, which contains information on the surveyed species.
```{r tidy = FALSE, echo = FALSE}
knitr::kable(
  raw_species_info,
  booktabs = TRUE
)
```

### Vigour measurements {}
The described columns are available in the data file `raw_vigmeasure_vigour.csv`, which contains information on vigour (growth, phenology) of the respective tussock at the observational units.
```{r tidy = FALSE, echo = FALSE}
knitr::kable(
  raw_vig,
  booktabs = TRUE
)
```

## Freezing experiments {}
### Electrolyte leakage {}
The described columns are available in the data file `raw_frostmeasure_freezingresistance.csv`, which contains information on freezing resistance of tissue samples from tussocks at the observational units as well as from an additional field site (transplant experiment).
```{r tidy = FALSE, echo = FALSE}
knitr::kable(
  raw_frost,
  booktabs = TRUE
)
```




