--- 
title: "Documentation master thesis"
author: "Raphael S. von Büren"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "Documentation of master thesis of Raphael S. von Büren, Department of Environmental Sciences, University of Basel. Supervised by Dr. Erika Hiltbrunner and Prof. Dr. Ansgar Kahmen."
---

```{r setup-index, include = FALSE, message = FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')

# Libraries
library(tidyverse)

# Read data
tbl.test <- readr::read_csv(file = "docs/GitHub-documentation_files/test.csv", col_names = T)
```


# Prerequisites

This is a **documentation book**, providing details on data structure and analyses of the the master thesis "Habitat-demands, micro-climate and freezing resistance of the tussock graminoids _Carex curvula_ and _Nardus stricta_".

The **bookdown** package, used to create this book, can be installed from CRAN or Github:

```{r eval = FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```




**The documentation was build with the following R version:**
```{r echo = FALSE, }
writeLines(R.version$version.string)
```